%کلمات کلیدی انگلیسی
\latinkeywords{Write a 3 to 5 KeyWords is essential. Example: AUT, M.Sc., Ph. D,..}
%چکیده انگلیسی

\en-abstract{
In recent years, machine learning—and in particular, deep neural networks—have made remarkable advancements, achieving near-human performance in fields such as computer vision, natural language processing, and speech recognition. Achieving such performance typically requires pre-training these networks on large-scale datasets, a process that enables the reuse of trained models across a variety of tasks. In many real-world applications, however, data becomes available incrementally and in the form of sequential tasks, highlighting the need for continual learning approaches. A major challenge in this domain is catastrophic forgetting, wherein the model suffers a significant drop in performance on previously learned tasks after acquiring new ones. Despite recent developments in large language models and vision-language models, limitations such as high memory consumption remain. This research introduces ProActionCLIP, a method for continual learning on video data that combines the feature extraction capabilities of the vision-language model Open-VCLIP with the learnable prompt mechanism from the L2P model. This integration enables adaptation to sequential tasks without altering the main parameters of the base Open-VCLIP model, while optimizing prompt selection to mitigate catastrophic forgetting. Experimental results demonstrate that the proposed method not only preserves prior knowledge and effectively learns new knowledge, but also offers high efficiency in terms of memory and computational resource usage. Consequently, it provides an effective solution for continual learning in human action recognition within video datasets.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Keywords:}}\par
\vspace*{.5cm}
Continual learning, vision-language model, prompt learning, catastrophic forgetting
\end{latin}